\section{State Feedback Control}

Tilstandsregulering (moderne regulering).


\subsection{Controllability (styrbarhed)}

Means if you can control your system to any desired state.

We cannot design a a controller for a system that is not controllable in this course.

A continuous time system
$$ \dot{x} = Ax(t) + Bu(t), x(0)=0 $$
is said to be controllable if and only if for any $\zeta \in \mathbb{R}^n$,
there exists $u(t)$ such that for some $T>0, x(T)=\zeta$




A discrete time system
$$x_{k+1} = \Phi x_k + \Gamma u_k, x_0=0$$
is said to be controllable if and only if for any $\zeta \in \mathbb{R}^n$, there exists
$(u_0, u_1, \cdots)$ such that for some $N>0, x_N=\zeta$

From iterating through the discrete time system, we get:
$$ x_n = \Phi^{n-1} \Gamma u_0 + \dots + \Phi \Gamma u_{n-2} + \Gamma u_{n-1} $$

The controllability matrix (styrbarheds matricen):
$$ x_n = \begin{bmatrix}  \Gamma & \Phi \Gamma & \cdots & \phi ^{n-1} \Gamma \end{bmatrix} $$

A system where $x \in \mathbb{R}^n, u \in \mathbb{R}^m$ is controlable if and only if the controllability
matrix has full rank.

In continuous time you look at the matrix:
$$ Rank \begin{bmatrix} B & AB & \cdots & A^{n-1}B \end{bmatrix} = n $$


Having only 1 input signal, the system is controllable if:
$$ \det \begin{Bmatrix} B & AB & \cdots & A^{n-1}B \end{Bmatrix} \neq 0 $$




\subsection{Controllable Cannonical Form}
Any controllable system can be transformed into a controllable cannonical form.
The reason as to doing so is to simplify the design of the state feedback controller.

Considering $n=3$ and introduce the following notation for the rows of $T^{-1}$:

$$T^{-1} = \begin{bmatrix}
		s_1 \\
		s_2 \\
		s_3
	\end{bmatrix} $$


$$A_c = T^{-1}AT$$
$$B_c = T^{-1}B$$
\subsection{State Feedback and Pole Assignment}
Tilstands regulator.


Eigen values of $(A+BF)$ is the poles of the closed loop system.
We can change F so $A+BF$ has any desired eigen values.

If the system is controllable and placed on controllable cannonical form, it is then possible
to place the poles of the closed loop system at any desired location using $F$.


$$F_c = \begin{bmatrix} a_{cl,1} - a_1 & ... & A_{cl,n} - a_n \end{bmatrix} $$
$$ F = F_c T^{-1}$$

\subsection{Examples}
