\section{Exam questions}

\textbf{Define concurrent and sequntial statements}

Concurrent statements are statements that are executed in parallel.
Sequential statements are statements that are executed in sequence.


\textbf{Which are the differences between conditional signal assignment and selected signal assignment?}

Selected signal assignments only have one assignment operator.
Thus, assignments are only based on the condition of the signal.

Conditional signal assignments are used for describing
statements that have only one target but can have more than
one associated expression assigned to it.



\textbf{What is the difference between a D-Latch and a D-Flip / Flop?}

A D latch works using an enable signal.
Where a D-Flip / Flop works using a clock signal.


\textbf{Difference between signals and variables}

Variables can only be used within a process. Where a signal
can be used both outside and within.

A signal is used for communicating betwen different processes
and for creating physical connections within a design.

A variable is used for storing data within a process.


\textbf{Explain how a counter/shift register works?}

A counter works by incrementing the value of a register.
This can be done by using a clock signal.

A shift register is a register which can shift its content
either left or right.


\textbf{How do keypad encoders work?}

Keypad encoders work by sending a signal to a row and then
look for a signal on the columns. If a signal is found
then a key has been pressed.


\textbf{Explain how half/full adders, subtraction, multipliers, and dividers work?}

Half adder is an addition block which takes two inputs and outputs
the sum and a carry bit.

A full adder is an addition block which takes a carry bit as input and
two other inputs and outputs the sum and a carry bit.

Subtraction can be done by using two's complement.

Multiplication can be done by using a series of additions.

Division can be done by multiplication and right shifting.


\textbf{What’s the difference between a Mealy and a Moore Machine?}

The mealy state machine has outputs that depend on the current state and the inputs.
Where a moore state machine only depend on the current state.

\textbf{How does the Electronic Door Lock work?}

It works by having a sequence detector built as a state machine.

\textbf{Explain the FPGA design flow (functional and timing, simulation, synthesis, place, and route, etc.).}




\textbf{What’s the difference between CPLDs and FPGAs?}

A CPLD is a complex programmable logic device.
This device has fewer logic blocks and more interconnect.
Logic blocks can only connect to the neighboring logic blocks.
Non-volatile memory is used to store the configuration.
CPLDs are good for simple applications and cheaper compared to FPGAs.

An FPGA is a field-programmable gate array.
This device is more versatile and has more logic blocks.
The memory is volatile and needs to be reprogrammed on every power cycle.




\textbf{Explain RAM/ROM and BRAM?}

RAM is random access memory.

ROM is read only memory.

BRAM is block RAM. This memory is used
for storing larger blocks of data, that could be from
a sensor.


\textbf{How do UART, SPI, and I2C work, and what are the main differences between them?}

UART is a universal asynchronous receiver-transmitter.

SPI is a serial peripheral interface is a synchronous serial communication
interface for short-distance communication.

I2C is an inter-integrated circuit is a multi-master, multi-slave communication.



\textbf{Hvordan kan man gøre sine VHDL-entities genbrugelige? Kom med et eksempel}

Man kan gøre sine VHDL entities genbrugelige ved at bruge generics.
Det kunne f.eks. være en counter med en generic størrelse.



\textbf{Hvad er forskellen på en latch og en flip-flop?}

En latch gemmer ved brug af et enable signal. En flip flop er clock afhængig.

\textbf{Hvordan tester man mere komplekse kredsløb I simulering?}

Ved brug af testbenches.
En testbench er et stykke kode, som du skriver i VHDL for at teste dit design.
Testbenchen simulerer inputsignaler og overvåger outputsignalerne for at verificere, at designet
fungerer korrekt.


\textbf{Beskriv strukturelt hvordan man implementerer en clock divider I VHDL}

You have a divisor that is used to divide the clock signal.
You then count to half of this value and then toggle the output signal.
By doing this twice it effectively divides the clock signal by the divisor.


\textbf{Hvad er forskellen på behavioral, post-synthesis, og post-implementation simulation?}

Behavioral simulering er brugt til at verificere funktionaliteten af desinget
uden at tage hensyn til hardwareimplementeringen.
Man ignorerer i dette stadie timing- og hardware specifikke detaljer som forsinkelser og fysiske
begrænsninger.

Post synthesis simulering er brugt til at verificere funktionaliteten af designet
efter syntesen. Bruges til at kontrollere, at synteseværktøjet har fortolket
og implementeret designet korrekt.

Post implementation tester designet efter placering og routing for at sikre, at designet
fungerer korekt med faktiske timing-forsinkelser og hardware-specifikke detaljer.


\textbf{Beskriv hvordan vi får vores færdigdesignede kredsløb til at køre på en FPGA}

Synthesis, place and route, program FPGA.


\textbf{Giv et eksempel på et FPGA system hvori man kan bruge en RAM}

Kunne være til at gemme pixeldata midlertidigt fra et kamera.






